appendix

### 2023-03-07 paper_comparison/appendix.Rmd
finish KL in appendix

## Effect size derivation and caculation

@@

$$KL = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')|}{|diag(\boldsymbol{R}_a\sigma^2)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}diag(\boldsymbol{R}_a\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}\boldsymbol{\mu}_z\right).$$

@@

@@

>>>>

## Effect size

## Derivation

@@

\begin{equation}
\label{eq:effect-size}
KL = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')|}{|diag(\boldsymbol{R}_a\sigma^2)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}diag(\boldsymbol{R}_a\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}\boldsymbol{\mu}_z\right).
\end{equation}

@@

## Caculation

The effect size can be calculated using Equation \ref{eq:effect-size} for each lineup by plugging in the data generated from the simulated model. However, since the term $\boldsymbol{R}_a$ will differ for each sample, the effect size will be different even if the parameter values are the same. To overcome this undesired property, for the same set of parameter values, we simulate a sufficient large number of samples, and take the average of the effect size as the final effect size.

@@

Mapping of subjects to experimental factors
